Ceph Parallel File System Evaluation Report

### 2013-11-06 ceph-initial.tex
cutting
more fixes based on the reviewer's comment

Our early testing indicated a read performace abberation.  There were periods of high performance followed by
periods of low performance or outright stalls that could last for up to 20
seconds at a time.  RADOS bench recorded poor read performance across
different backend file systems, as shown in
Figure~\ref{fig:rados-tcp-autotune}.

@@

We measured performance at the client (using RADOS bench) for one to four OSD
servers.  Each additional OSD server adds eleven
more OSDs into play.  Figure~\ref{fig:oss-scale} demonstrates that read
performance improved about 10\% given eight clients instead of four, but write
performance is mostly flat.  The lost write performance compared to a single
OSD is attributed to Ceph journaling.  Ceph does not support meta-data only
journaling, therefore every write is the equivalent of a double-write: once to
the data device, once to the journaling device.  It is unclear why read
performance is so much lower than the theoretical maximum.
%This effectively cuts the observed system bandwidth in
%half. 
%That said, it does not explain the read performance -- it is a little
%better than write, but still far from the theoretical maximum.
%Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
%performance improved about 10\% given eight clients instead of four, but write
%performance is mostly flat for reason explained below. We also observe that
%Ceph exhibits linear scaling with regard to number of servers, at least in the
%given number of servers.  However, the peak performance we are seeing is about
%the half of what are expecting from the SFA10K (compare to the baseline block
%I/O performance number presented in Section~\ref{sec:block-io}).
%
%For writes, the lost performance is attributed to the way Ceph performs
%journaling: Ceph does not support meta-data only journaling, therefore every
%write is the equivalent of a double-write: once to the data device, once to
%the journaling device. This effectively cuts the observed system bandwidth in
%half. That said, it does not explain the read performance -- it is a little
%better than write, but still far from the theoretical maximum.

@@

\begin{figure*}[!t]

\centerline{\subfloat[4 KB transfer size]
{\includegraphics[width=3in]{data/ior_4k}
\label{fig:ior4k}}
\hfil
\subfloat[4 MB transfer size]
{\includegraphics[width=3in]{data/ior_4m}
\label{fig:ior4m}}
}% end of centerline
\caption{CephFS scalability test with IOR}

\end{figure*}

>>>>

Our early testing indicated a read performace abberation.  There were periods
of high performance followed by periods of low performance or outright stalls
that could last for up to 20 seconds at a time.  RADOS bench recorded poor
read performance across different backend file systems, as shown in
Figure~\ref{fig:rados-tcp-autotune}.\footnote{Although we conducted this
particular experiment with three different flavors of local file system, with
BTRFS the best performer, Inktank however doesn't think BTRFS is
production-ready yet. So when not explicitly stated, the follow-on experiments
use XFS by default.}

@@

We measured performance at the client (using RADOS bench) for one to four OSD
servers. Each additional OSD server adds eleven more OSDs into play. Based on
Figure~\ref{fig:osd-scale}, the perfect scaling projects the aggregated read
with 4 OSSs should be at 6616 MB/s and write at 5640 MB/s.
Figure~\ref{fig:oss-scale} demonstrates that both read and write
\textit{scales} with increasing number of OSSs, but at a loss of 13.6\% and
16.0\% respectively. We will discuss the improvement to this result through
parameter probing.

%Figure~\ref{fig:oss-scale} demonstrates that read
%performance improved about 10\% given eight clients instead of four, but write
%performance is mostly flat.  The lost write performance compared to a single
%OSD is attributed to Ceph journaling.  Ceph does not support meta-data only
%journaling, therefore every write is the equivalent of a double-write: once to
%the data device, once to the journaling device.  It is unclear why read
%performance is so much lower than the theoretical maximum.

%This effectively cuts the observed system bandwidth in
%half. 
%That said, it does not explain the read performance -- it is a little
%better than write, but still far from the theoretical maximum.
%Comparing to Figure~\ref{fig:rados-tcp-autotune-disabled}, the read
%performance improved about 10\% given eight clients instead of four, but write
%performance is mostly flat for reason explained below. We also observe that
%Ceph exhibits linear scaling with regard to number of servers, at least in the
%given number of servers.  However, the peak performance we are seeing is about
%the half of what are expecting from the SFA10K (compare to the baseline block
%I/O performance number presented in Section~\ref{sec:block-io}).
%
%For writes, the lost performance is attributed to the way Ceph performs
%journaling: Ceph does not support meta-data only journaling, therefore every
%write is the equivalent of a double-write: once to the data device, once to
%the journaling device. This effectively cuts the observed system bandwidth in
%half. That said, it does not explain the read performance -- it is a little
%better than write, but still far from the theoretical maximum.

@@

\begin{figure}[!t]

\centerline{\subfloat[4 KB transfer size]
%{\includegraphics[width=3in]{data/ior_4k}
{\includegraphics[width=1.7in]{data/ior_4k}
\label{fig:ior4k}}
\hfil
\subfloat[4 MB transfer size]
%{\includegraphics[width=3in]{data/ior_4m}
{\includegraphics[width=1.7in]{data/ior_4m}
\label{fig:ior4m}}
}% end of centerline
\caption{CephFS scalability test with IOR}

\end{figure}

### 2013-11-06 ceph-tuning.tex
more fixes based on the reviewer's comment

As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4
MB.  These results are illustrated in Figure~\ref{fig:ior-064}, respectively.
As expected, we saw saw  improved read and write performance. These new read
and write performance are in line with observed RADOS bench performance.

@@

Throughout our IOR testing, we observed that the average write throughput is
lower than the maximum.  This behavior was observed during other tests as well,
indicating that we may have periods of time where write throughput is
temporarily degrading.  Despite these issues, performance generally seems to be
improving with respect to increasing number of clients.  Writes seem to be
topping out at around 5.2 GB/s (which is roughly what we would expect due to
journalling effectively halving the write performance).  Reads seem to be
topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
would continue scaling with more clients and get closer to ~8 GB/s we observed 
with RADOS Bench.

>>>>

As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4
MB.  These results are illustrated in Figure~\ref{fig:ior-064}, respectively.
As expected, we saw both improved read and write performance. These new read
and write performance are in line with observed RADOS bench performance.

@@

%Throughout our IOR testing, we observed that the average write throughput is
%lower than the maximum.  
% This behavior was observed during other tests as well,
%indicating that we may have periods of time where write throughput is
%temporarily degrading.  Despite these issues, performance generally seems to be
%improving with respect to increasing number of clients.

Writes seem to be topping out at around 5.2 GB/s (which is roughly what we
would expect due to journaling effectively halving the write performance).
Reads seem to be topping out anywhere from 5.6-7 GB/s, however it is unclear
if read performance would continue scaling with more clients and get closer to
8 GB/s we observed with RADOS Bench.
